---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# jazz

<!-- badges: start -->
<!-- badges: end -->

The goal of jazz is to ... `r emo::ji("sax")` `r emo::ji("musical notes")`

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(jazz)
library(tidyselect)

g <- dplyr::group_by(iris, Species)

# that's a bit like dplyr::summarise 
g %>% 
  jazz(
    Sepal.Length = ~ mean(Sepal.Length), 
    Sepal.Width  = ~ mean(Sepal.Width) 
  )

# however it's using formulas instead of quosures
# and similarly to rap it can empower the lhs of the formula, 
g %>% 
  jazz(
    Sepal.Length = character() ~ mean(Sepal.Length)
  )

# the rhs of the formula can make tibbles too 
# the only requirement is that the vec_size() 
# of the output has to be 1
g %>% 
  jazz(
    Sepal =  ~ tibble(Sepal.Length = mean(Sepal.Length), Sepal.Width = mean(Sepal.Width))
  )
```

### swing

There's no `jazz_at()` or `jazz_if()` but you can use `swing()` if you want to 
use the same function for a bunch of columns: 

```{r}
g %>% 
  jazz(
    !!!swing(mean, ends_with("th"))
  )
```

aaaand you actually do not need to `!!!`, this works as well : 

```{r}
g %>% 
  jazz(
    swing(mean, ends_with("th"))
  )
```

The results are named after the names of the input columns, i.e. 

```{r}
tidyselect::vars_select(tbl_vars(g), ends_with("th"))
```

The `.name` gives you a way to control the names by means 
of a glue pattern: 

```{r}
g %>% 
  jazz(
    swing(mean, starts_with("Petal"), .name = "mean_{var}"),
    swing(median, starts_with("Petal"), .name = "median_{var}")
  )
```

The first argument of `swing()` is a function, or a formula: 

```{r}
g %>% 
  jazz(
    swing(~mean(., na.rm = TRUE), starts_with("Petal"), .name = "mean_{var}")
  )
```

